---
title: "Test/Train Serial TMA Sections - Tau"
author: "Claire S. Peterson"
date: "10/31/2019"
output:
  pdf_document: default
  html_document: null
  toc: yes
  toc_depth: 5
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)

library(ggplot2)  #data visualization
library(BlandAltmanLeh)
library(readxl)   #read excel files
library(stargazer)  #print out clean tables
library(matrixStats)
library(corrplot)
library(gridExtra)
library(dplyr)
library(ggExtra)
library(blandr)
library(tinytex)
library(ggpubr)

# Create function for calculating correlations and outputting lower triangle correlation matrices ####
lower.tri.cor.matrix <- function(df){
  cor.matrix<-round(cor(df, use = "complete.obs"), 3)
  cor.matrix[upper.tri(cor.matrix)]<-""
  cor.matrix<-as.data.frame(cor.matrix)
  cor.matrix
  
  return(cor.matrix)
}
#####     CV VALUES    #####
inter.assay.cv <- function(df, ...){
  grp_vars <- quos(...)
  selected.cols <- df %>%
    select(!!!grp_vars)
  dat.as.matrix <- as.matrix(selected.cols)
  selected.cols$mean <- rowMeans(selected.cols,na.rm = T)
  selected.cols$sd <- rowSds(dat.as.matrix,na.rm = T)
  selected.cols <- selected.cols %>%
    mutate(CV = sd/mean,
           pct.CV = (sd/mean)*100)
  
  return(selected.cols)
}

#setwd("~/Desktop/Work-IrwinLab/TMA Scripts and data/TMA Data and scripts 8_21")

setwd("U:/TMA/Custom Algorithm - Tau")

tau_df_halo_raw<- read.csv("Run 2 custom alg.csv")   # Import your dataset
names(tau_df_halo_raw)

tau_df_halo_raw_with_cores <- tau_df_halo_raw
    # # this is the number of rows which have absolute zero %AO
    # abszero<-tau_df_halo_raw %>%
    #   filter_all(any_vars(.==0.00)) %>%
    #   count()

```

### **Sampling with replacement (train n=94, test n=95)***

<!-- ##### **Tau TMA Raw Summary**  -->
<!-- ```{r  Raw summary, echo=FALSE} -->
<!-- stargazer(as.data.frame(tau_df_halo_raw), title = "Summary of TMA Tau Raw", type='text')  # Print summary of AO (contains Mean, SD, Min/Max, and Quartiles, type = "text") -->
<!-- ``` -->

<!-- # ```{r converts all 0 %AO to NA, echo=FALSE, include=FALSE} -->
<!-- # # Changes 0 %AO values to NA -->
<!-- # tau_df_halo_raw[tau_df_halo_raw==0]<- "NA" -->
<!-- # # Ensure all columns are numerics... this is necessary to ln transform data -->
<!-- # tau_df_halo_raw[,c(2,4)]<- sapply(tau_df_halo_raw[,c(2,4)], as.numeric) -->
<!-- # raw_values <- tau_df_halo_raw[,c(2,4)] -->
<!-- # # Confirm all 0 %AO values are changed to NA -->
<!-- # checkabszero <- tau_df_halo_raw %>% -->
<!-- #   filter_all(any_vars(.==0.00)) %>% -->
<!-- #   count() -->
<!-- # ##add cores back to raw values -->
<!-- # raw_values$CORES <- tau_df_halo_raw$CORES -->
<!-- # ``` -->


####** ln Transform Data**
```{r, echo=FALSE, include=FALSE}
raw_values <- tau_df_halo_raw[,c(2,4,6)]
# then proceed to ln transform data
#### LOG TRANSFORMED DATA ####
tau_df_halo_LOG<- log(tau_df_halo_raw[,c(2,4,6)])
# removes any absolute zeros resulting from transformation
tau_df_halo_LOG$CORES <- tau_df_halo_raw$CORES
transformed_values <- tau_df_halo_LOG
```

##### **Tau TMA ln Transformed Summary** 
```{r ln transformed summary, echo=FALSE}
    # stargazer(as.data.frame(tau_df_halo_LOG), title = "Summary of TMA Tau ln Transformed", type='text')  # Print summary of AO (contains Mean, SD, Min/Max, and Quartiles, type = "text")
# changes column names of transformed values to have ln prefix
colnames(transformed_values) <- paste("ln", colnames(transformed_values), sep = "_")
is.na(transformed_values) <- sapply(transformed_values, is.infinite)
# creates combine dataset with raw values
alldat <- cbind(tau_df_halo_raw_with_cores$R2S1, raw_values, transformed_values)

alldat <- cbind(tau_df_halo_raw_with_cores$R2S1, raw_values, transformed_values)
colnames(alldat)[colnames(alldat)=="tau_df_halo_raw_with_cores$R2S1"] <- "Core"
```

<!-- ### **Tau TMA Normality Visual Inspection** -->
<!-- ```{r qqplot and histograms normality inspection, echo=FALSE} -->
<!-- ### R2 S1 -->
<!-- par(mfrow=c(1,2))                  # Raw -->
<!-- qqnorm(tau_df_halo_raw$R2S1.AO) -->
<!-- hist(tau_df_halo_raw$R2S1.AO, -->
<!--      main = "Histogram of Raw R2S1", -->
<!--      xlab = "R2S1") -->
<!-- par(oma=c(0,0,2,0)) -->
<!-- title("Raw R2S1" , outer=TRUE) -->
<!-- par(mfrow=c(1,2))                  # ln Transformed -->
<!-- qqnorm(tau_df_halo_LOG$R2S1.AO) -->
<!-- hist(tau_df_halo_LOG$R2S1.AO, -->
<!--      main = "Histogram of ln(R2S1)", -->
<!--      xlab = "R2_S1") -->
<!-- par(oma=c(0,0,2,0)) -->
<!-- title("ln Transformed R2S1" , outer=TRUE) -->
<!-- ### R2 S2 -->
<!-- par(mfrow=c(1,2))                  # Raw -->
<!-- qqnorm(tau_df_halo_raw$R2S2.AO) -->
<!-- hist(tau_df_halo_raw$R2S2.AO, -->
<!--      main = "Histogram of Raw R2S2", -->
<!--      xlab = "R2S2") -->
<!-- par(oma=c(0,0,2,0)) -->
<!-- title("Raw R2S2" , outer=TRUE) -->
<!-- par(mfrow=c(1,2))                  # ln Transformed -->
<!-- qqnorm(tau_df_halo_LOG$R2S2.AO) -->
<!-- hist(tau_df_halo_LOG$R2S2.AO, -->
<!--      main = "Histogram of ln(R2S2)", -->
<!--      xlab = "R2S2") -->
<!-- par(oma=c(0,0,2,0)) -->
<!-- title("ln Transformed R2S2" , outer=TRUE) -->
<!-- ### R2 S3 -->
<!-- par(mfrow=c(1,2))                  # Raw -->
<!-- qqnorm(tau_df_halo_raw$R2S3.AO) -->
<!-- hist(tau_df_halo_raw$R2S3.AO, -->
<!--      main = "Histogram of Raw R2S3", -->
<!--      xlab = "R2_S3") -->
<!-- par(oma=c(0,0,2,0)) -->
<!-- title("Raw R2S3" , outer=TRUE) -->
<!-- par(mfrow=c(1,2))                  # ln Transformed -->
<!-- qqnorm(tau_df_halo_LOG$R2S3.AO) -->
<!-- hist(tau_df_halo_LOG$R2S3.AO, -->
<!--      main = "Histogram of ln(R2S3)", -->
<!--      xlab = "R2S3") -->
<!-- par(oma=c(0,0,2,0)) -->
<!-- title("ln Transformed R2S3" , outer=TRUE) -->
<!-- ``` -->

###**Only work with ln transformed data from this point on**  
####_Split data with 100 training cores_
```{r training data, echo=FALSE}
set.seed(999)
# randomly split dataset into training subset of 30 data points and complementary testing subset. train = control data wich is included in each TMA, test = remainder to test on
split <- sample(nrow(alldat),replace=F,size=0.5*nrow(alldat))
train <- alldat[split, ]
test <- alldat[-split, ]
#print summary of all columns in training dataset
stargazer(as.data.frame(train), type = "text", title = "Summary of Training Data")
# Removes TMA Core name from df
train_ln_only <- train[,c(2:7)]
test_ln_only <- test[,c(2:7)]

```
#### *Correlation Matrix of Tau* `r knitr::kable(lower.tri.cor.matrix(train_ln_only[,1:6]))`

```{r, echo=FALSE}
# Run 2 Only - create columns of differences between runs/slides
train_ln_only$r2s1_r2s2_diff <- train_ln_only$ln_R2S1.AO - train_ln_only$ln_R2S2.AO #S1-S2
train_ln_only$r2s2_r2s3_diff <- train_ln_only$ln_R2S2.AO - train_ln_only$ln_R2S3.AO #S2-S3
train_ln_only$r2s1_r2s3_diff <- train_ln_only$ln_R2S1.AO - train_ln_only$ln_R2S3.AO #S1-S3

train_diff <- train_ln_only[c("r2s1_r2s2_diff", "r2s2_r2s3_diff", "r2s1_r2s3_diff")]
stargazer(as.data.frame(train_diff), type = "text", title = "Summary of Training Differences")
```

```{r t tests/regression on untransformed training data, echo=FALSE, include=FALSE}
# t test on differences
r2s1_r2s2.t.test <- t.test(train_diff$r2s1_r2s2_diff, mu = 0) #S1-S2
r2s2_r2s3.t.test <- t.test(train_diff$r2s2_r2s3_diff, mu = 0) #S2-S3
r2s1_r2s3.t.test <- t.test(train_diff$r2s1_r2s3_diff, mu = 0) #S1-S3

          # # regress run 1 slides by run 2/run 3 slides - RUN 1 = dependent variable
          #     LINEAR TRANSFORMATION TO STAINING BATCH - NO LONGER USED (10/31/2019)
          # r1.r2.s1.reg <- lm(train_ln_only$ln_R1_S1 ~ train_ln_only$ln_R2_S1)
          # summary(r1.r2.s1.reg)
          # r1.r3.s1.reg <- lm(train_ln_only$ln_R1_S1 ~ train_ln_only$ln_R3_S1)
          # summary(r1.r3.s1.reg)
          # r1.r2.s2.reg <- lm(train_ln_only$ln_R1_S2 ~ train_ln_only$ln_R2_S2)
          # summary(r1.r2.s2.reg)
          # r1.r3.s2.reg <- lm(train_ln_only$ln_R1_S2 ~ train_ln_only$ln_R3_S2)
          # summary(r1.r3.s2.reg)
```

<!-- # **Cook's D - Remove outliers/influential points** -->
<!-- ```{r Cooks D} -->
<!-- # Create new datasets of 2 staining batch comparisons and exclude NAs - this ensures there will a consistent number of rows between the datasets -->
<!-- r1.r2.s1.df <- na.omit(train_ln_only[,c("ln_R1_S1", "ln_R2_S1")]) -->
<!-- r1.r3.s1.df <- na.omit(train_ln_only[,c("ln_R1_S1", "ln_R3_S1")]) -->
<!-- r1.r2.s2.df <- na.omit(train_ln_only[,c("ln_R1_S2", "ln_R2_S2")]) -->
<!-- r1.r3.s2.df <- na.omit(train_ln_only[,c("ln_R1_S2", "ln_R3_S2")]) -->

<!-- # Cook's D cutoff for exclusion is estimated as 4/n -->
<!-- cooksD_cutoff.r1.r2.s1 <- 4/((nrow(r1.r2.s1.df))) -->
<!-- cooksD_cutoff.r1.r3.s1 <- 4/((nrow(r1.r3.s1.df))) -->
<!-- cooksD_cutoff.r1.r2.s2 <- 4/((nrow(r1.r2.s2.df))) -->
<!-- cooksD_cutoff.r1.r3.s2 <- 4/((nrow(r1.r3.s2.df))) -->

<!-- # Cook's D plot shows influential outliers (higher values in the plot) -->
<!-- plot(r1.r2.s1.reg, which=4, cook.levels=GM_cutoff) -->
<!-- plot(r1.r3.s1.reg, which=4, cook.levels=GM_cutoff) -->
<!-- plot(r1.r2.s2.reg, which=4, cook.levels=GM_cutoff) -->
<!-- plot(r1.r3.s2.reg, which=4, cook.levels=GM_cutoff) -->

<!-- # Create new variable with Cook's D value for all data points in dataset -->
<!-- r1.r2.s1.df$cooksD <- cooks.distance(r1.r2.s1.reg) -->
<!-- r1.r3.s1.df$cooksD <- cooks.distance(r1.r3.s1.reg) -->
<!-- r1.r2.s2.df$cooksD <- cooks.distance(r1.r2.s2.reg) -->
<!-- r1.r3.s2.df$cooksD <- cooks.distance(r1.r3.s2.reg) -->

<!-- # Obtain revised dataset without outliers, i.e. keep only values with low Cook's D < 4/n -->
<!-- r1.r2.s1.df_rev <- subset(r1.r2.s1.df, r1.r2.s1.df$cooksD < cooksD_cutoff) -->
<!-- r1.r3.s1.df_rev <- subset(r1.r3.s1.df, r1.r3.s1.df$cooksD < cooksD_cutoff) -->
<!-- r1.r2.s2.df_rev <- subset(r1.r2.s2.df, r1.r2.s2.df$cooksD < cooksD_cutoff) -->
<!-- r1.r3.s2.df_rev <- subset(r1.r3.s2.df, r1.r3.s2.df$cooksD < cooksD_cutoff) -->

<!-- # Rerun linear model anew w/o outliers -->
<!-- r1.r2.s1.reg_rev <- lm(ln_R1_S1 ~ ln_R2_S1, r1.r2.s1.df_rev) -->
<!-- summary(r1.r2.s1.reg_rev) -->
<!-- r1.r3.s1.reg_rev <- lm(ln_R1_S1 ~ ln_R3_S1, r1.r3.s1.df_rev) -->
<!-- summary(r1.r3.s1.reg_rev) -->
<!-- r1.r2.s2.reg_rev <- lm(ln_R1_S2 ~ ln_R2_S2, r1.r2.s2.df_rev) -->
<!-- summary(r1.r2.s2.reg_rev) -->
<!-- r1.r3.s2.reg_rev <- lm(ln_R1_S2 ~ ln_R3_S2, r1.r3.s2.df_rev) -->
<!-- summary(r1.r3.s2.reg_rev) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Transforms run 2 values to run 1  - slide 1 -->
<!-- train_ln_only$ln_R2_S1_t <-  coef(summary(r1.r2.s1.reg_rev))[2, 1]  * train_ln_only$ln_R2_S1 + coef(summary(r1.r2.s1.reg_rev))[1, 1] -->
<!-- # Transforms run 3 values to run 1 - slide 1 -->
<!-- train_ln_only$ln_R3_S1_t <-  coef(summary(r1.r3.s1.reg_rev))[2, 1]  * train_ln_only$ln_R3_S1 + coef(summary(r1.r3.s1.reg_rev))[1, 1] -->
<!-- # Transforms run 2 values to run 1 - slide 2 -->
<!-- train_ln_only$ln_R2_S2_t <-  coef(summary(r1.r2.s2.reg_rev))[2, 1]  * train_ln_only$ln_R2_S2 + coef(summary(r1.r2.s2.reg_rev))[1, 1] -->
<!-- # Transforms run 3 values to run 1 - slide 2 -->
<!-- train_ln_only$ln_R3_S2_t <-  coef(summary(r1.r3.s2.reg_rev))[2, 1]  * train_ln_only$ln_R3_S2 + coef(summary(r1.r3.s2.reg_rev))[1, 1] -->


<!-- # create of  columns of transformed differences between runs/slides -->
<!-- # Slide 1 -->
<!-- train_ln_only$r1_r2.s1_diff_t <- train_ln_only$ln_R1_S1 - train_ln_only$ln_R2_S1_t -->
<!-- train_ln_only$r1_r3.s1_diff_t <- train_ln_only$ln_R1_S1 - train_ln_only$ln_R3_S1_t -->
<!-- # Slide 2 -->
<!-- train_ln_only$r1_r2.s2_diff_t <- train_ln_only$ln_R1_S2 - train_ln_only$ln_R2_S2_t -->
<!-- train_ln_only$r1_r3.s2_diff_t <- train_ln_only$ln_R1_S2 - train_ln_only$ln_R3_S2_t -->
<!-- # print summary of transformed differences -->
<!-- train_diff_t <- train_ln_only[c("r1_r2.s1_diff_t", "r1_r3.s1_diff_t", "r1_r2.s2_diff_t", "r1_r3.s2_diff_t")] -->

<!-- # t test on differences in testing set -->
<!-- r1_r2.s1_diff_t.test_t <- t.test(train_diff_t$r1_r2.s1_diff_t, mu = 0) -->
<!-- r1_r3.s1_diff_t.test_t <- t.test(train_diff_t$r1_r3.s1_diff_t, mu = 0) -->
<!-- r1_r2.s2_diff_t.test_t <- t.test(train_diff_t$r1_r2.s2_diff_t, mu = 0) -->
<!-- r1_r3.s2_diff_t.test_t <- t.test(train_diff_t$r1_r3.s2_diff_t, mu = 0) -->
<!-- ``` -->


<!-- ## *Transform training values to Run 1* -->
<!-- ```{r verify transformation works in training dataset, echo=FALSE} -->
<!-- stargazer(as.data.frame(train_diff_t), type = "text", title = "Summary of Transformed Training Differences") -->
<!-- ``` -->

```{r, echo=FALSE, include=FALSE}
########### cv Calculations for Training Data-for verfication 
# Slide 2 - 3 Combinations 
# ln Transformed
ln.R2.S1.S2.CV <- inter.assay.cv(train_ln_only, ln_R2S1.AO, ln_R2S2.AO)
ln.R2.S2.S3.CV <- inter.assay.cv(train_ln_only, ln_R2S2.AO, ln_R2S3.AO)
ln.R2.S1.S3.CV <- inter.assay.cv(train_ln_only, ln_R2S1.AO, ln_R2S3.AO)
# Raw Transformed
R2.S1.S2.CV <- inter.assay.cv(train_ln_only, R2S1.AO, R2S2.AO)
R2.S2.S3.CV <- inter.assay.cv(train_ln_only, R2S2.AO, R2S3.AO)
R2.S1.S3.CV <- inter.assay.cv(train_ln_only, R2S1.AO, R2S3.AO)

```

```{r AVG CV COMPARISION TRAINING DATA}
# ln Transformed
mean(ln.R2.S1.S2.CV$pct.CV, na.rm = T)
mean(ln.R2.S2.S3.CV$pct.CV, na.rm = T)
mean(ln.R2.S1.S3.CV$pct.CV, na.rm = T)
# Raw
mean(R2.S1.S2.CV$pct.CV, na.rm = T)
mean(R2.S2.S3.CV$pct.CV, na.rm = T)
mean(R2.S1.S3.CV$pct.CV, na.rm = T)

```


```{r BA Plots - training data untransformed and transformed, echo=FALSE}
# Serial Intraassay - Run 2
    # Slide 1 vs Slide 2
r2_s1.s2_ba_stats <- bland.altman.stats(train_ln_only$ln_R2S1.AO , train_ln_only$ln_R2S2.AO)
r2_s1.s2_ba_plot <- {plot(r2_s1.s2_ba_stats$means, r2_s1.s2_ba_stats$diffs,
     sub=paste("Mean Bias is",r2_s1.s2_ba_stats$mean.diffs, "and the P-Value is", r2s1_r2s2.t.test$p.value),
     main="ln Tau Run 2 Slides 1 v. 2", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = r2_s1.s2_ba_stats$lines, col=c("red","blue","red"))}

    # Slide 2 vs Slide 3
r2_s2.s3_ba_stats <- bland.altman.stats(train_ln_only$ln_R2S2.AO , train_ln_only$ln_R2S3.AO)
r2_s2.s3_ba_plot <- {plot(r2_s2.s3_ba_stats$means, r2_s2.s3_ba_stats$diffs,
     sub=paste("Mean Bias is",r2_s2.s3_ba_stats$mean.diffs, "and the P-Value is", r2s2_r2s3.t.test$p.value),
     main="ln Tau Run 2 Slides 2 v. 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = r2_s2.s3_ba_stats$lines, col=c("red","blue","red"))}

    # Slide 1 vs Slide 3
r2_s1.s3_ba_stats <- bland.altman.stats(train_ln_only$ln_R2S1.AO , train_ln_only$ln_R2S3.AO)
r2_s1.s3_ba_plot <- {plot(r2_s1.s3_ba_stats$means, r2_s1.s3_ba_stats$diffs,
     sub=paste("Mean Bias is",r2_s1.s3_ba_stats$mean.diffs, "and the P-Value is", r2s1_r2s3.t.test$p.value),
     main="ln Tau Run 2 Slides 1 v. 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = r2_s1.s3_ba_stats$lines, col=c("red","blue","red"))}
```


# **Testing data on remaining 50% cores**


#### *Correlation Matrix of Tau* `r knitr::kable(lower.tri.cor.matrix(test_ln_only[,1:6]))`

```{r, echo=FALSE}
# Run 2 Only - create columns of differences between runs/slides
test_ln_only$r2s1_r2s2_diff <- test_ln_only$ln_R2S1.AO - test_ln_only$ln_R2S2.AO #S1-S2
test_ln_only$r2s2_r2s3_diff <- test_ln_only$ln_R2S2.AO - test_ln_only$ln_R2S3.AO #S2-S3
test_ln_only$r2s1_r2s3_diff <- test_ln_only$ln_R2S1.AO - test_ln_only$ln_R2S3.AO #S1-S3

test_diff <- test_ln_only[c("r2s1_r2s2_diff", "r2s2_r2s3_diff", "r2s1_r2s3_diff")]
stargazer(as.data.frame(train_diff), type = "text", title = "Summary of Testing Differences")
```

```{r t tests/regression on testing data, echo=FALSE, include=FALSE}
# t test on differences
r2s1_r2s2.t.test <- t.test(test_diff$r2s1_r2s2_diff, mu = 0) #S1-S2
r2s2_r2s3.t.test <- t.test(test_diff$r2s2_r2s3_diff, mu = 0) #S2-S3
r2s1_r2s3.t.test <- t.test(test_diff$r2s1_r2s3_diff, mu = 0) #S1-S3

          # # regress run 1 slides by run 2/run 3 slides - RUN 1 = dependent variable
          #     LINEAR TRANSFORMATION TO STAINING BATCH - NO LONGER USED (10/31/2019)
          # r1.r2.s1.reg <- lm(test_ln_only$ln_R1_S1 ~ test_ln_only$ln_R2_S1)
          # summary(r1.r2.s1.reg)
          # r1.r3.s1.reg <- lm(test_ln_only$ln_R1_S1 ~ test_ln_only$ln_R3_S1)
          # summary(r1.r3.s1.reg)
          # r1.r2.s2.reg <- lm(test_ln_only$ln_R1_S2 ~ test_ln_only$ln_R2_S2)
          # summary(r1.r2.s2.reg)
          # r1.r3.s2.reg <- lm(test_ln_only$ln_R1_S2 ~ test_ln_only$ln_R3_S2)
          # summary(r1.r3.s2.reg)
```

```{r, echo=FALSE, include=FALSE}
########### cv Calculations for Training Data-for verfication 
# Slide 2 - 3 Combinations 
# ln Transformed
ln.R2.S1.S2.CV <- inter.assay.cv(test_ln_only, ln_R2S1.AO, ln_R2S2.AO)
ln.R2.S2.S3.CV <- inter.assay.cv(test_ln_only, ln_R2S2.AO, ln_R2S3.AO)
ln.R2.S1.S3.CV <- inter.assay.cv(test_ln_only, ln_R2S1.AO, ln_R2S3.AO)
# Raw Transformed
R2.S1.S2.CV <- inter.assay.cv(test_ln_only, R2S1.AO, R2S2.AO)
R2.S2.S3.CV <- inter.assay.cv(test_ln_only, R2S2.AO, R2S3.AO)
R2.S1.S3.CV <- inter.assay.cv(test_ln_only, R2S1.AO, R2S3.AO)

```

```{r AVG CV COMPARISION testing DATA}
# ln Transformed
mean(ln.R2.S1.S2.CV$pct.CV, na.rm = T)
mean(ln.R2.S2.S3.CV$pct.CV, na.rm = T)
mean(ln.R2.S1.S3.CV$pct.CV, na.rm = T)
# Raw
mean(R2.S1.S2.CV$pct.CV, na.rm = T)
mean(R2.S2.S3.CV$pct.CV, na.rm = T)
mean(R2.S1.S3.CV$pct.CV, na.rm = T)

```


```{r BA Plots - testing data, echo=FALSE}
# Serial Intraassay - Run 2
    # Slide 1 vs Slide 2
r2_s1.s2_ba_stats <- bland.altman.stats(train_ln_only$ln_R2S1.AO , train_ln_only$ln_R2S2.AO)
r2_s1.s2_ba_plot <- {plot(r2_s1.s2_ba_stats$means, r2_s1.s2_ba_stats$diffs,
     sub=paste("Mean Bias is",r2_s1.s2_ba_stats$mean.diffs, "and the P-Value is", r2s1_r2s2.t.test$p.value),
     main="Testing Data - ln Tau Run 2 Slides 1 v. 2", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = r2_s1.s2_ba_stats$lines, col=c("red","blue","red"))}

    # Slide 2 vs Slide 3
r2_s2.s3_ba_stats <- bland.altman.stats(train_ln_only$ln_R2S2.AO , train_ln_only$ln_R2S3.AO)
r2_s2.s3_ba_plot <- {plot(r2_s2.s3_ba_stats$means, r2_s2.s3_ba_stats$diffs,
     sub=paste("Mean Bias is",r2_s2.s3_ba_stats$mean.diffs, "and the P-Value is", r2s2_r2s3.t.test$p.value),
     main="Testing Data - ln Tau Run 2 Slides 2 v. 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = r2_s2.s3_ba_stats$lines, col=c("red","blue","red"))}

    # Slide 1 vs Slide 3
r2_s1.s3_ba_stats <- bland.altman.stats(train_ln_only$ln_R2S1.AO , train_ln_only$ln_R2S3.AO)
r2_s1.s3_ba_plot <- {plot(r2_s1.s3_ba_stats$means, r2_s1.s3_ba_stats$diffs,
     sub=paste("Mean Bias is",r2_s1.s3_ba_stats$mean.diffs, "and the P-Value is", r2s1_r2s3.t.test$p.value),
     main="Testing Data - ln Tau Run 2 Slides 1 v. 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = r2_s1.s3_ba_stats$lines, col=c("red","blue","red"))}
```
## **Training Scatter plots**
```{r scatterplots for testing, echo=FALSE }
####    Inter-assay plots - untransformed training data    ####
# Slide 2
r2.s1.s2.scatplot<- ggplot(data = train_ln_only, aes(x = ln_R2S1.AO, y = ln_R2S2.AO)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("Run 2 Slide 1 %AO") + ylab("Run 2 Slide 2 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10))
r2.s2.s3.scatplot<- ggplot(data = train_ln_only, aes(x = ln_R2S2.AO, y = ln_R2S3.AO)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("Run 2 Slide 2 %AO") + ylab("Run 2 Slide 3 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10))
r2.s1.s3.scatplot<- ggplot(data = train_ln_only, aes(x = ln_R2S1.AO, y = ln_R2S3.AO)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("Run 2 Slide 1 %AO") + ylab("Run 2 Slide 3 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10))

# Prints Inter-assay Scatter Plots Together  #
#-------------------------------------------------------------------
run2.ln.trainplot <- ggarrange(r2.s1.s2.scatplot, r2.s2.s3.scatplot, r2.s1.s3.scatplot, ncol = 2, nrow = 2)
annotate_figure(run2.ln.trainplot, top = text_grob("ln Training Data Tau",  face = "bold", size = 16))
ggsave("run2.ln.trainplot.tau_TMA.png")
```


## **Testing Scatter plots**
```{r scatterplots for testing samples before and after transformation, echo=FALSE }
####    Inter-assay plots - untransformed training data    ####
# Slide 2
r2.s1.s2.scatplot<- ggplot(data = test_ln_only, aes(x = ln_R2S1.AO, y = ln_R2S2.AO)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("Run 2 Slide 1 %AO") + ylab("Run 2 Slide 2 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10))
r2.s2.s3.scatplot<- ggplot(data = test_ln_only, aes(x = ln_R2S2.AO, y = ln_R2S3.AO)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("Run 2 Slide 2 %AO") + ylab("Run 2 Slide 3 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10))
r2.s1.s3.scatplot<- ggplot(data = test_ln_only, aes(x = ln_R2S1.AO, y = ln_R2S3.AO)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("Run 2 Slide 1 %AO") + ylab("Run 2 Slide 3 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10))

# Prints Inter-assay Scatter Plots Together  #
#-------------------------------------------------------------------
run2.ln.testplot <- ggarrange(r2.s1.s2.scatplot, r2.s2.s3.scatplot, r2.s1.s3.scatplot, ncol = 2, nrow = 2)
annotate_figure(run2.ln.testplot, top = text_grob("ln testing Data Tau",  face = "bold", size = 16))
ggsave("run2.ln.testplot.tau_TMA.png")
```

<!-- #### Intra-assay validation -->
<!-- ```{r intra validation, echo=FALSE} -->

<!--     # Slide 1 -->
<!-- test_ln_only$r1_s1.s2_diff <- test_ln_only$ln_R1_S1 - test_ln_only$ln_R1_S2 -->
<!--     # Slide 2 -->
<!-- test_ln_only$r2_s1.s2_diff <- test_ln_only$ln_R2_S1 - test_ln_only$ln_R2_S2 -->
<!-- test_ln_only$r2_s2.s3_diff <- test_ln_only$ln_R2_S2 - test_ln_only$ln_R3_S3 -->
<!-- test_ln_only$r2_s1.s3_diff <- test_ln_only$ln_R2_S1 - test_ln_only$ln_R2_S3 -->
<!--     # Slide 3 -->
<!-- test_ln_only$r3_s1.s2_diff <- test_ln_only$ln_R3_S1 - test_ln_only$ln_R3_S2 -->
<!-- test_ln_only$r3_s2.s3_diff <- test_ln_only$ln_R3_S2 - test_ln_only$ln_R3_S3 -->
<!-- test_ln_only$r3_s1.s3_diff <- test_ln_only$ln_R3_S1 - test_ln_only$ln_R3_S3 -->



<!-- r1s1s2 <- t.test(test_ln_only$r1_s1.s2_diff, mu = 0) -->
<!-- #Run 2 -->
<!-- r2s1s2 <- t.test(test_ln_only$r2_s1.s2_diff, mu = 0) -->
<!-- r2s2s3 <- t.test(test_ln_only$r2_s2.s3_diff, mu = 0) -->
<!-- r2s1s3 <- t.test(test_ln_only$r2_s1.s3_diff, mu = 0) -->
<!-- # Run 3 -->
<!-- r3s1s2 <- t.test(test_ln_only$r3_s1.s2_diff, mu = 0)  -->
<!-- r3s2s3 <- t.test(test_ln_only$r3_s2.s3_diff, mu = 0)  -->
<!-- r3s1s3 <- t.test(test_ln_only$r3_s1.s3_diff, mu = 0) -->

<!-- # Intra-assay Scatter Plots  # -->
<!-- #-------------------------------------------------- -->
<!-- # Run 1 Plot -->
<!-- r1.1v2_LOG <- ggplot(data = test_ln_only, aes(x = ln_R1_S1, y = ln_R1_S2)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("SB1.S1 %AO") + ylab("SB1.S2 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 20, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10)) -->
<!-- # Run 2 Plot (1v2) -->
<!-- r2.1v2_LOG <- ggplot(data = test_ln_only, aes(x = ln_R2_S1, y = ln_R2_S2)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("SB2.S1 %AO") + ylab("SB2.S2 %AO") +  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10)) -->
<!-- # Run 2 Plot (2v3) -->
<!-- r2.2v3_LOG <- ggplot(data = test_ln_only, aes(x = ln_R2_S2, y = ln_R2_S3)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("SB2.S2 %AO") + ylab("SB2.S3 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10)) -->
<!-- # Run 2 Plot (1v3) -->
<!-- r2.1v3_LOG <- ggplot(data = test_ln_only, aes(x = ln_R2_S1, y = ln_R2_S3)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("SB2.S1 %AO") + ylab("SB2.S3 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10)) -->
<!-- # Run 3 Plot (1v2) -->
<!-- r3.1v2_LOG <- ggplot(data = test_ln_only, aes(x = ln_R3_S1, y = ln_R3_S2)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("SB3.S1 %AO") + ylab("SB3.S2 %AO") +  theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10)) -->
<!-- # Run 3 Plot (2v3) -->
<!-- r3.2v3_LOG <- ggplot(data = test_ln_only, aes(x = ln_R3_S2, y = ln_R3_S3)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("SB3.S2 %AO") + ylab("SB3.S3 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10)) -->
<!-- # Run 3 Plot (1v3) -->
<!-- r3.1v3_LOG <- ggplot(data = test_ln_only, aes(x = ln_R3_S1, y = ln_R3_S3)) + geom_point(size = 2, colour = "blue") + geom_smooth(method = "lm", colour = "red", se = FALSE) + xlab("SB3.S1 %AO") + ylab("SB3.S3 %AO") + theme(axis.title = element_text(size = 10), axis.text = element_text(size = 10), plot.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 10), legend.title = element_text(size = 10)) -->

<!-- untransformed_intra <- ggarrange(r1.1v2_LOG, ncol = 1, nrow = 3)  -->
<!-- annotate_figure(untransformed_intra, top = text_grob("Testing Untransformed Intra-assay Run 1- tau",  face = "bold", size = 10)) -->
<!-- ggsave("Testing Untransformed Intra-assay Run 1- tau.png") -->
<!-- untransformed2_intra <- ggarrange(r2.1v3_LOG, r2.1v2_LOG, r2.2v3_LOG, ncol = 1, nrow = 3) -->
<!-- annotate_figure(untransformed2_intra, top = text_grob("Testing Untransformed Intra-assay Run 2 - tau",  face = "bold", size = 10)) -->
<!-- ggsave("Testing Untransformed Intra-assay Run 2- tau.png") -->
<!-- untransformed3_intra <- ggarrange(r3.1v3_LOG, r3.1v2_LOG, r3.2v3_LOG, ncol = 1, nrow = 3)  -->
<!-- annotate_figure(untransformed3_intra, top = text_grob("Testing Untransformed Intra-assay Run 3- tau",  face = "bold", size = 10)) -->
<!-- ggsave("Testing Untransformed Intra-assay Run 3- tau.png") -->


<!-- # BA PLOTS --------------- -->
<!-- # Run 1 intra-assay -->
<!-- r1.s1.s2_ba_stats <- bland.altman.stats(test_ln_only$ln_R1_S1 , test_ln_only$ln_R1_S2) -->
<!-- r1.s1.s2_ba_plot <- {plot(r1.s1.s2_ba_stats$means, r1.s1.s2_ba_stats$diffs, -->
<!--      sub=paste("Mean Bias is",r1.s1.s2_ba_stats$mean.diffs, "and the P-Value is", r1s1s2$p.value), -->
<!--      main="Testing Untransformed Tau Run 1 Intra-assay", pch = 19, xlab = "Means", ylab = "Differences") -->
<!-- abline(h = r1.s1.s2_ba_stats$lines, col=c("red","blue","red"))} -->
<!-- # Run 2 intra-assay -->
<!-- r2.s1.s2_ba_stats <- bland.altman.stats(test_ln_only$ln_R2_S1 , test_ln_only$ln_R2_S2) -->
<!-- r2.s1.s2_ba_plot <- {plot(r2.s1.s2_ba_stats$means, r2.s1.s2_ba_stats$diffs, -->
<!--      sub=paste("Mean Bias is",r2.s1.s2_ba_stats$mean.diffs, "and the P-Value is", r2s1s2$p.value), -->
<!--      main="Testing Untransformed Tau Run 2 - Slides 1 vs 3", pch = 19, xlab = "Means", ylab = "Differences") -->
<!-- abline(h = r2.s1.s2_ba_stats$lines, col=c("red","blue","red"))} -->
<!-- r2.s1.s3_ba_stats <- bland.altman.stats(test_ln_only$ln_R2_S2 , test_ln_only$ln_R2_S3) -->
<!-- r2.s1.s3_ba_plot <- {plot(r2.s1.s3_ba_stats$means, r2.s1.s3_ba_stats$diffs, -->
<!--      sub=paste("Mean Bias is",r2.s1.s3_ba_stats$mean.diffs, "and the P-Value is", r2s1s3$p.value), -->
<!--      main="Testing Untransformed tau Run 2 - Slides 2 vs 3", pch = 19, xlab = "Means", ylab = "Differences") -->
<!-- abline(h = r2.s1.s3_ba_stats$lines, col=c("red","blue","red"))} -->
<!-- # Run 2 intra-assay -->
<!-- r3.s1.s2_ba_stats <- bland.altman.stats(test_ln_only$ln_R3_S1 , test_ln_only$ln_R3_S2) -->
<!-- r3.s1.s2_ba_plot <- {plot(r3.s1.s2_ba_stats$means, r3.s1.s2_ba_stats$diffs, -->
<!--      sub=paste("Mean Bias is",r3.s1.s2_ba_stats$mean.diffs, "and the P-Value is", r3s1s2$p.value), -->
<!--      main="Testing Untransformed Tau Run 3 - Slides 1 vs 2", pch = 19, xlab = "Means", ylab = "Differences") -->
<!-- abline(h = r3.s1.s2_ba_stats$lines, col=c("red","blue","red"))} -->
<!-- r3.s1.s3_ba_stats <- bland.altman.stats(test_ln_only$ln_R3_S2 , test_ln_only$ln_R3_S3) -->
<!-- r3.s1.s3_ba_plot <- {plot(r3.s1.s3_ba_stats$means, r3.s1.s3_ba_stats$diffs, -->
<!--      sub=paste("Mean Bias is",r3.s1.s3_ba_stats$mean.diffs, "and the P-Value is", r3s1s3$p.value), -->
<!--      main="Testing Untransformed tau Run 3 - Slides 2 vs 3", pch = 19, xlab = "Means", ylab = "Differences") -->
<!-- abline(h = r3.s1.s3_ba_stats$lines, col=c("red","blue","red"))} -->


<!-- r1.s1.s2_large_differences <- test_ln_only[,c("CORES","ln_R1_S1","ln_R1_S2","r1_s1.s2_diff")] -->
<!-- r1.s1.s2_large_differences <- r1.s1.s2_large_differences %>% filter(r1_s1.s2_diff>5) -->
<!-- r1.s1.s2_large_differences -->


<!-- ``` -->


<!-- #Investigate Training and Testing Outliers -->
<!-- ```{r, echo=FALSE} -->
<!-- #RUN 2 INTRA ASSAY -->
<!-- r2.s1.s2.cv <- inter.assay.cv(test_ln_only, ln_R2_S1, ln_R2_S2) -->
<!-- #names(r2.s1.s2.cv) <- c("R2_S1", "R2_S2", "R2.1V2_mean", "R2.1V2_sd", "R2.1V2_CV", "R2.1V2_pct.CV") -->
<!-- r2.s1.s2.cv$CORES <- test_ln_only$CORES -->
<!-- r2.s1.s3.cv <- inter.assay.cv(test_ln_only, ln_R2_S1, ln_R2_S3) -->
<!-- #names(r2.s1.s3.cv) <- c("R2_S1", "R2_S3", "R2.1V3_mean", "R2.1V3_sd", "R2.1V3_CV", "R2.1V3_pct.CV") -->
<!-- r2.s1.s3.cv$CORES <- test_ln_only$CORES -->
<!-- r2.s2.s3.cv <- inter.assay.cv(test_ln_only, ln_R2_S2, ln_R2_S3) -->
<!-- #names(r2.s2.s3.cv) <- c("R2_S1", "R2_S3", "R2.2V3_mean", "R2.2V3_sd", "R2.2V3_CV", "R2.2V3_pct.CV") -->
<!-- r2.s2.s3.cv$CORES <- test_ln_only$CORES -->
<!-- r2.s1.s2.s3.cv <- inter.assay.cv(test_ln_only, ln_R2_S1, ln_R2_S2, ln_R2_S3) -->
<!-- r2.s1.s2.s3.cv$CORES <- test_ln_only$CORES -->

<!-- intra2.1v2v3.large.cv <- r2.s1.s2.s3.cv %>% select(CORES, pct.CV) %>% filter(pct.CV>40) -->
<!-- intra2.1v2.large.cv <- r2.s1.s2.cv %>% select(CORES, pct.CV) %>% filter(pct.CV>40) -->
<!-- intra2.1v3.large.cv <- r2.s1.s3.cv %>% select(CORES, pct.CV) %>% filter(pct.CV>40) -->
<!-- intra2.2v3.large.cv <- r2.s2.s3.cv %>% select(CORES, pct.CV) %>% filter(pct.CV>40) -->

<!-- # find cores that have consistent high variation -->
<!-- highly.varied <- rbind(intra1.large.cv, intra2.1v2v3.large.cv, intra2.1v2.large.cv, intra2.1v3.large.cv, intra2.2v3.large.cv, intra3.1v2v3.large.cv, intra3.1v2.large.cv, intra3.1v3.large.cv, intra3.2v3.large.cv) -->

<!-- highly.varied %>% group_by(CORES) %>% count_() -->
<!-- highly.varied %>% group_by(CORES)     # These are the cores with the actual %CVs -->

<!-- intra1.large.cv <- r1.s1.s2.cv %>% filter(pct.CV>40) -->
<!-- intra2.1v2v3.large.cv <- r2.s1.s2.s3.cv %>% filter(pct.CV>40) -->
<!-- intra2.1v2.large.cv <- r2.s1.s2.cv %>%  filter(pct.CV>40) -->
<!-- intra2.1v3.large.cv <- r2.s1.s3.cv %>% filter(pct.CV>40) -->
<!-- intra2.2v3.large.cv <- r2.s2.s3.cv %>% filter(pct.CV>40) -->
<!-- intra3.1v2v3.large.cv <- r3.s1.s2.s3.cv %>% filter(pct.CV>40) -->
<!-- intra3.1v2.large.cv <- r3.s1.s2.cv %>% filter(pct.CV>40) -->
<!-- intra3.1v3.large.cv <- r3.s1.s3.cv %>% filter(pct.CV>40) -->
<!-- intra3.2v3.large.cv <- r3.s2.s3.cv %>% filter(pct.CV>40) -->

<!-- intra1.large.cv -->
<!-- intra2.1v2v3.large.cv -->
<!-- intra2.1v2.large.cv -->
<!-- intra2.1v3.large.cv -->
<!-- intra2.2v3.large.cv -->
<!-- intra3.1v2v3.large.cv -->
<!-- intra3.1v2.large.cv -->
<!-- intra3.1v3.large.cv -->
<!-- intra3.2v3.large.cv -->

<!-- ``` -->


```{r, echo=FALSE}
# Run 2 Only - create columns of differences between runs/slides
train$r2s1_r2s2_diff <- train$R2S1.AO - train$R2S2.AO #S1-S2
train$r2s2_r2s3_diff <- train$R2S2.AO - train$R2S3.AO #S2-S3
train$r2s1_r2s3_diff <- train$R2S1.AO - train$R2S3.AO #S1-S3

train_diff <- train[c("r2s1_r2s2_diff", "r2s2_r2s3_diff", "r2s1_r2s3_diff")]
stargazer(as.data.frame(train_diff), type = "text", title = "Summary of Training Differences")
```

```{r t tests/regression on untransformed training data, echo=FALSE, include=FALSE}
# t test on differences
r2s1_r2s2.t.test <- t.test(train_diff$r2s1_r2s2_diff, mu = 0) #S1-S2
r2s2_r2s3.t.test <- t.test(train_diff$r2s2_r2s3_diff, mu = 0) #S2-S3
r2s1_r2s3.t.test <- t.test(train_diff$r2s1_r2s3_diff, mu = 0) #S1-S3

          # # regress run 1 slides by run 2/run 3 slides - RUN 1 = dependent variable
          #     LINEAR TRANSFORMATION TO STAINING BATCH - NO LONGER USED (10/31/2019)
          # r1.r2.s1.reg <- lm(train_ln_only$ln_R1_S1 ~ train_ln_only$ln_R2_S1)
          # summary(r1.r2.s1.reg)
          # r1.r3.s1.reg <- lm(train_ln_only$ln_R1_S1 ~ train_ln_only$ln_R3_S1)
          # summary(r1.r3.s1.reg)
          # r1.r2.s2.reg <- lm(train_ln_only$ln_R1_S2 ~ train_ln_only$ln_R2_S2)
          # summary(r1.r2.s2.reg)
          # r1.r3.s2.reg <- lm(train_ln_only$ln_R1_S2 ~ train_ln_only$ln_R3_S2)
          # summary(r1.r3.s2.reg)
```


