---
title: "TMA Custom Alg."
author: "Claire S. Peterson"
date: "11/8/2019"
output: pdf_document
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)

library(ggplot2)  #data visualization
library(BlandAltmanLeh)
library(readxl)   #read excel files
library(stargazer)  #print out clean tables
library(matrixStats)
library(corrplot)
library(gridExtra)
library(dplyr)
library(ggExtra)
library(blandr)
library(tinytex)
library(ggpubr)
library(broom)
library(purrr)
# Create function for calculating correlations and outputting lower triangle correlation matrices ####
lower.tri.cor.matrix <- function(df){
  cor.matrix<-round(cor(df, use = "complete.obs"), 3)
  cor.matrix[upper.tri(cor.matrix)]<-""
  cor.matrix<-as.data.frame(cor.matrix)
  cor.matrix
  
  return(cor.matrix)
}
#####     CV VALUES    #####
inter.assay.cv <- function(df, ...){
  grp_vars <- quos(...)
  selected.cols <- df %>%
    select(!!!grp_vars)
  dat.as.matrix <- as.matrix(selected.cols)
  selected.cols$mean <- rowMeans(selected.cols,na.rm = T)
  selected.cols$sd <- rowSds(dat.as.matrix,na.rm = T)
  selected.cols <- selected.cols %>%
    mutate(CV = sd/mean,
           pct.CV = (sd/mean)*100)
  
  return(selected.cols)
}

format.t.test <- function(df){
 df <- df[c("estimate", "p.value", "parameter")]
df$comparison <- c("ln training","raw training","ln testing", "raw testing","ln fixed training","raw fixed training","ln fixed testing", "raw fixed testing")
df <- df[c("comparison", "estimate", "p.value", "parameter")]
colnames(df)[colnames(df)=="parameter"] <- "DF" 
return(df)
}
#setwd("~/Desktop/Work-IrwinLab/TMA Scripts and data/TMA Data and scripts 8_21")

setwd("U:/TMA/Custom Algorithm - Tau")

tau_df_halo_raw <- read.csv("U:/TMA/Custom Algorithm - Tau/serial slides 12 and 13 clean.csv")   # Import your dataset

tau_df_halo_raw_with_cores <- tau_df_halo_raw

```


```{r}
tau_df_halo_raw$difference = tau_df_halo_raw$slide12.ao - tau_df_halo_raw$slide13.ao
large_differences <- tau_df_halo_raw %>%
  select(slide12, difference) %>%
  filter(difference>10)

train <- large_differences[split, ]
test <- alldat[-split, ]
subset (tau_df_halo_raw$slide12  large_differences$slide12)

```



### **Sampling with replacement (train n=94, test n=95)***

####** ln Transform Data**
```{r, echo=FALSE, include=FALSE}
raw_values <- tau_df_halo_raw[,c(2,4)]
# then proceed to ln transform data
#### LOG TRANSFORMED DATA ####
tau_df_halo_LOG<- log(tau_df_halo_raw[,c(2,4)])
# removes any absolute zeros resulting from transformation
tau_df_halo_LOG$CORES <- tau_df_halo_raw$CORES
transformed_values <- tau_df_halo_LOG
```

 
```{r, echo=FALSE}
    # stargazer(as.data.frame(tau_df_halo_LOG), title = "Summary of TMA Tau ln Transformed", type='text')  # Print summary of AO (contains Mean, SD, Min/Max, and Quartiles, type = "text")
# changes column names of transformed values to have ln prefix
colnames(transformed_values) <- paste("ln", colnames(transformed_values), sep = "_")
is.na(transformed_values) <- sapply(transformed_values, is.infinite)
# creates combine dataset with raw values
alldat <- cbind(tau_df_halo_raw_with_cores$slide12, raw_values, transformed_values)

alldat <- cbind(tau_df_halo_raw_with_cores$slide12, raw_values, transformed_values)
colnames(alldat)[colnames(alldat)=="tau_df_halo_raw_with_cores$slide12"] <- "Core"
```

###**Only work with ln transformed data from this point on**  
####_Split data with 100 training cores_
```{r data, echo=FALSE}
set.seed(999)
# randomly split dataset into training subset of 30 data points and complementary testing subset. train = control data wich is included in each TMA, test = remainder to test on
split <- sample(nrow(alldat),replace=F,size=0.5*nrow(alldat))
train <- alldat[split, ]
test <- alldat[-split, ]
#print summary of all columns in training dataset
stargazer(as.data.frame(train), type = "text", title = "Summary of Training Data")
# Removes TMA Core name from df
train_ln_only <- train[,c(2:5)]
test_ln_only <- test[,c(2:5)]

```
#### *Correlation Matrix of Tau* `r knitr::kable(lower.tri.cor.matrix(train[,2:5]))`

```{r, echo=FALSE}
train$ln_slide12_slide13_diff <- train$ln_slide12.ao - train$ln_slide13.ao #S1-S2
train$slide12_slide13_diff <- train$slide12.ao - train$slide13.ao #S1-S2

train_diff <- train[c("ln_slide12_slide13_diff", "slide12_slide13_diff")]
stargazer(as.data.frame(train_diff), type = "text", title = "Summary of Training Differences")
```

```{r t tests/regression on untransformed training data, echo=FALSE, include=FALSE}
# t test on differences

train.slide12_slide13.t.test <- t.test(train_diff$slide12_slide13_diff, mu = 0) 
train.ln.slide12_slide13.t.test <- t.test(train_diff$ln_slide12_slide13_diff, mu = 0) 
```

```{r, echo=FALSE, include=FALSE}
########### cv Calculations for Training Data-for verfication 
# Slide 2 - 3 Combinations 
# ln Transformed
train.ln.12.13.CV <- inter.assay.cv(train, ln_slide12.ao, ln_slide13.ao)
# Raw Transformed
train.raw.12.13.CV <- inter.assay.cv(train, slide12.ao, slide13.ao)

```

```{r AVG CV COMPARISION TRAINING DATA}
# ln Transformed
train.ln_avg.cv <- mean(train.ln.12.13.CV$pct.CV, na.rm = T)
# Raw
train.raw_avg.cv <- mean(train.raw.12.13.CV$pct.CV, na.rm = T)
```
```{r BA Plots - training data untransformed and transformed, echo=FALSE}
# Serial Intraassay - Run 2
# ln transformed values
train.ln.12.13.ba_stats <- bland.altman.stats(train$ln_slide12.ao , train$ln_slide13.ao)
train.ln.r2_s1.s2_ba_plot <- {plot(train.ln.12.13.ba_stats$means, train.ln.12.13.ba_stats$diffs,
     main="ln Tau Training Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
  abline(h = train.ln.12.13.ba_stats$lines, col=c("red","blue","red"))}

# Raw values
train.raw.12.13.ba_stats <- bland.altman.stats(train$slide12.ao , train$slide13.ao)
train.r2_s1.s2_ba_plot <- {plot(train.raw.12.13.ba_stats$means, train.raw.12.13.ba_stats$diffs,
     main="Raw Tau Training Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
  abline(h = train.raw.12.13.ba_stats$lines, col=c("red","blue","red"))}

# par(mfrow = c(2, 1)) # Create a 2 x 2 plotting matrix
# {plot(raw.12.13.ba_stats$means, raw.12.13.ba_stats$diffs,
#      main="Raw Tau Training Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
# abline(h = raw.12.13.ba_stats$lines, col=c("red","blue","red"))}
# {plot(ln.12.13.ba_stats$means, ln.12.13.ba_stats$diffs,
#      main="ln Tau Training Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
# abline(h = ln.12.13.ba_stats$lines, col=c("red","blue","red"))}
```



# **Testing data on remaining 50% cores**

#### *Correlation Matrix of Tau* `r knitr::kable(lower.tri.cor.matrix(test[,2:5]))`

```{r, echo=FALSE}
test$ln_slide12_slide13_diff <- test$ln_slide12.ao - test$ln_slide13.ao #S1-S2
test$slide12_slide13_diff <- test$slide12.ao - test$slide13.ao #S1-S2

test_diff <- test[c("ln_slide12_slide13_diff", "slide12_slide13_diff")]
stargazer(as.data.frame(test_diff), type = "text", title = "Summary of testing Differences")
```

```{r, include=FALSE}
# t test on differences
test.slide12_slide13.t.test <- t.test(test_diff$slide12_slide13_diff, mu = 0) 
test.ln.slide12_slide13.t.test <- t.test(test_diff$ln_slide12_slide13_diff, mu = 0) 
```

```{r, echo=FALSE, include=FALSE}
########### cv Calculations for testing Data-for verfication 
# Slide 2 - 3 Combinations 
# ln Transformed
test.ln.12.13.CV <- inter.assay.cv(test, ln_slide12.ao, ln_slide13.ao)
# Raw Transformed
test.raw.12.13.CV <- inter.assay.cv(test, slide12.ao, slide13.ao)

```

```{r AVG CV COMPARISION testING DATA}
# ln Transformed
test.ln_avg.cv <- mean(test.ln.12.13.CV$pct.CV, na.rm = T)
# Raw
test.raw_avg.cv <- mean(test.raw.12.13.CV$pct.CV, na.rm = T)
```

```{r BA Plots - testing data untransformed and transformed, echo=FALSE}
# Serial Intraassay - Run 2
# ln transformed values
test.ln.12.13.ba_stats <- bland.altman.stats(test$ln_slide12.ao , test$ln_slide13.ao)
test.ln.r2_s1.s2_ba_plot <- {plot(test.ln.12.13.ba_stats$means, test.ln.12.13.ba_stats$diffs,
     main="ln Tau testing Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = test.ln.12.13.ba_stats$lines, col=c("red","blue","red"))}
# Raw values
test.raw.12.13.ba_stats <- bland.altman.stats(test$slide12.ao , test$slide13.ao)
test.r2_s1.s2_ba_plot <- {plot(test.raw.12.13.ba_stats$means, test.raw.12.13.ba_stats$diffs,
     main="Raw Tau testing Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = test.raw.12.13.ba_stats$lines, col=c("red","blue","red"))}

# par(mfrow = c(2, 1)) # Create a 2 x 2 plotting matrix
# {plot(raw.12.13.ba_stats$means, raw.12.13.ba_stats$diffs,
#      main="Raw Tau testing Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
# abline(h = raw.12.13.ba_stats$lines, col=c("red","blue","red"))}
# {plot(ln.12.13.ba_stats$means, ln.12.13.ba_stats$diffs,
#      main="ln Tau testing Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
# abline(h = ln.12.13.ba_stats$lines, col=c("red","blue","red"))}
```





# *AT8 Fixed Algorithm*
```{r}
setwd("U:/TMA")
tau_df_halo_raw <- read_excel("Tau TMA AT8 Alg. Data.xlsx")   # Import your dataset
tau_df_halo_raw_with_cores <- tau_df_halo_raw
```

### **Sampling with replacement (train n=94, test n=95)***

####** ln Transform Data**
```{r, echo=FALSE, include=FALSE}
raw_values <- tau_df_halo_raw[,c(2,4)]
# then proceed to ln transform data
#### LOG TRANSFORMED DATA ####
tau_df_halo_LOG<- log(tau_df_halo_raw[,c(2,4)])
# removes any absolute zeros resulting from transformation
tau_df_halo_LOG$CORES <- tau_df_halo_raw$CORES
transformed_values <- tau_df_halo_LOG
```

##### **Tau TMA ln Transformed Summary** 
```{r}
    # stargazer(as.data.frame(tau_df_halo_LOG), title = "Summary of TMA Tau ln Transformed", type='text')  # Print summary of AO (contains Mean, SD, Min/Max, and Quartiles, type = "text")
# changes column names of transformed values to have ln prefix
colnames(transformed_values) <- paste("ln", colnames(transformed_values), sep = "_")
is.na(transformed_values) <- sapply(transformed_values, is.infinite)
# creates combine dataset with raw values
alldat <- cbind(tau_df_halo_raw_with_cores$slide12, raw_values, transformed_values)

alldat <- cbind(tau_df_halo_raw_with_cores$slide12, raw_values, transformed_values)
colnames(alldat)[colnames(alldat)=="tau_df_halo_raw_with_cores$slide12"] <- "Core"
```

###**Only work with ln transformed data from this point on**  
####_Split data with 100 training cores_
```{r}
# randomly split dataset into training subset of 30 data points and complementary testing subset. train = control data wich is included in each TMA, test = remainder to test on
split <- sample(nrow(alldat),replace=F,size=0.5*nrow(alldat))
train <- alldat[split, ]
test <- alldat[-split, ]
#print summary of all columns in training dataset
stargazer(as.data.frame(train), type = "text", title = "Summary of Training Data")
# Removes TMA Core name from df
train_ln_only <- train[,c(2:5)]
test_ln_only <- test[,c(2:5)]

```
#### *Correlation Matrix of Tau* `r knitr::kable(lower.tri.cor.matrix(train[,2:5]))`

```{r, echo=FALSE}
train$ln_slide12_slide13_diff <- train$ln_slide12.ao - train$ln_slide13.ao #S1-S2
train$slide12_slide13_diff <- train$slide12.ao - train$slide13.ao #S1-S2

train_diff <- train[c("ln_slide12_slide13_diff", "slide12_slide13_diff")]
stargazer(as.data.frame(train_diff), type = "text", title = "Summary of Training Differences")
```

```{r}
# t test on differences

train.fixed.slide12_slide13.t.test <- t.test(train_diff$slide12_slide13_diff, mu = 0) 
train.fixed.ln.slide12_slide13.t.test <- t.test(train_diff$ln_slide12_slide13_diff, mu = 0) 
```


```{r, echo=FALSE, include=FALSE}
########### cv Calculations for Training Data-for verfication 
# Slide 2 - 3 Combinations 
# ln Transformed
train.fixed.ln.12.13.CV <- inter.assay.cv(train, ln_slide12.ao, ln_slide13.ao)
# Raw Transformed
train.fixed.raw.12.13.CV <- inter.assay.cv(train, slide12.ao, slide13.ao)

```

```{r}
# ln Transformed
train.fixed.ln_avg.cv <- mean(train.fixed.ln.12.13.CV$pct.CV, na.rm = T)
# Raw
train.fixed.raw_avg.cv <- mean(train.fixed.raw.12.13.CV$pct.CV, na.rm = T)
```

```{r}
# Serial Intraassay - Run 2
# ln transformed values
train.fixed.ln.12.13.ba_stats <- bland.altman.stats(train$ln_slide12.ao , train$ln_slide13.ao)
train.fixed.ln.r2_s1.s2_ba_plot <- {plot(train.fixed.ln.12.13.ba_stats$means, train.fixed.ln.12.13.ba_stats$diffs,
     main="ln Tau Training Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = train.fixed.ln.12.13.ba_stats$lines, col=c("red","blue","red"))}
# Raw values
train.fixed.raw.12.13.ba_stats <- bland.altman.stats(train$slide12.ao , train$slide13.ao)
train.fixed.r2_s1.s2_ba_plot <- {plot(train.fixed.raw.12.13.ba_stats$means, train.fixed.raw.12.13.ba_stats$diffs,
     main="Raw Tau Training Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = train.fixed.raw.12.13.ba_stats$lines, col=c("red","blue","red"))}

# par(mfrow = c(2, 1)) # Create a 2 x 2 plotting matrix
# {plot(raw.12.13.ba_stats$means, raw.12.13.ba_stats$diffs,
#      main="Raw Tau Training Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
# abline(h = raw.12.13.ba_stats$lines, col=c("red","blue","red"))}
# {plot(ln.12.13.ba_stats$means, ln.12.13.ba_stats$diffs,
#      main="ln Tau Training Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
# abline(h = ln.12.13.ba_stats$lines, col=c("red","blue","red"))}
```



# **Testing data on remaining 50% cores**

#### *Correlation Matrix of Tau* `r knitr::kable(lower.tri.cor.matrix(test[,2:5]))`

```{r, echo=FALSE}
test$ln_slide12_slide13_diff <- test$ln_slide12.ao - test$ln_slide13.ao #S1-S2
test$slide12_slide13_diff <- test$slide12.ao - test$slide13.ao #S1-S2

test_diff <- test[c("ln_slide12_slide13_diff", "slide12_slide13_diff")]
stargazer(as.data.frame(test_diff), type = "text", title = "Summary of testing Differences")
```

```{r, echo=FALSE}
# t test on differences
test.fixed.slide12_slide13.t.test <- t.test(test_diff$slide12_slide13_diff, mu = 0) 
test.fixed.ln.slide12_slide13.t.test <- t.test(test_diff$ln_slide12_slide13_diff, mu = 0) 
```

```{r, echo=FALSE, include=FALSE}
########### cv Calculations for testing Data-for verfication 
# Slide 2 - 3 Combinations 
# ln Transformed
test.fixed.ln.12.13.CV <- inter.assay.cv(test, ln_slide12.ao, ln_slide13.ao)
# Raw Transformed
test.fixed.raw.12.13.CV <- inter.assay.cv(test, slide12.ao, slide13.ao)

```

```{r, echo=FALSE}
# ln Transformed
test.fixed.ln_avg.cv <- mean(test.fixed.ln.12.13.CV$pct.CV, na.rm = T)
# Raw
test.fixed.raw_avg.cv <- mean(test.fixed.raw.12.13.CV$pct.CV, na.rm = T)
```

```{r, echo=FALSE}
# Serial Intraassay - Run 2
# ln transformed values
test.fixed.ln.12.13.ba_stats <- bland.altman.stats(test$ln_slide12.ao , test$ln_slide13.ao)
test.fixed.ln.r2_s1.s2_ba_plot <- {plot(test.fixed.ln.12.13.ba_stats$means, test.fixed.ln.12.13.ba_stats$diffs,
     main="ln Tau testing Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = test.fixed.ln.12.13.ba_stats$lines, col=c("red","blue","red"))}
# Raw values
test.fixed.raw.12.13.ba_stats <- bland.altman.stats(test$slide12.ao , test$slide13.ao)
test.fixed.r2_s1.s2_ba_plot <- {plot(test.fixed.raw.12.13.ba_stats$means, test.fixed.raw.12.13.ba_stats$diffs,
     main="Raw Tau testing Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
abline(h = test.fixed.raw.12.13.ba_stats$lines, col=c("red","blue","red"))}

# par(mfrow = c(2, 1)) # Create a 2 x 2 plotting matrix
# {plot(raw.12.13.ba_stats$means, raw.12.13.ba_stats$diffs,
#      main="Raw Tau testing Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
# abline(h = raw.12.13.ba_stats$lines, col=c("red","blue","red"))}
# {plot(ln.12.13.ba_stats$means, ln.12.13.ba_stats$diffs,
#      main="ln Tau testing Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
# abline(h = ln.12.13.ba_stats$lines, col=c("red","blue","red"))}
```



```{r, echo=FALSE}
cvs <- c("train.ln_avg.cv", "train.raw_avg.cv", "test.ln_avg.cv", "test.raw_avg.cv")#"train.fixed.ln_avg.cv", "train.fixed.raw_avg.cv", "test.fixed.ln_avg.cv", "test.fixed.raw_avg.cv"
cvs <- rbind(train.ln_avg.cv, train.raw_avg.cv, test.ln_avg.cv, test.raw_avg.cv) #train.fixed.ln_avg.cv, train.fixed.raw_avg.cv, test.fixed.ln_avg.cv, test.fixed.raw_avg.cv
colnames(cvs) <- "Mean CV"
cvs
```
####Combine T-Tests from all datasets
```{r, echo=FALSE}
t.tests <- map_df(list(train.ln.slide12_slide13.t.test, train.slide12_slide13.t.test, test.ln.slide12_slide13.t.test, test.slide12_slide13.t.test, train.fixed.ln.slide12_slide13.t.test, train.fixed.slide12_slide13.t.test, test.fixed.ln.slide12_slide13.t.test, test.fixed.slide12_slide13.t.test), tidy)

total.tau.t.tests <- format.t.test(t.tests)
# train.ln.r2_s1.s2_ba_plot
# train.r2_s1.s2_ba_plot
# test.ln.r2_s1.s2_ba_plot
# test.r2_s1.s2_ba_plot
# train.fixed.ln.r2_s1.s2_ba_plot
# train.fixed.r2_s1.s2_ba_plot
# test.fixed.ln.r2_s1.s2_ba_plot
# test.fixed.r2_s1.s2_ba_plot
```

#### *TMA T-Test Output* `r knitr::kable(total.tau.t.tests)`



#*TEST ON ALL DATA*
#### *Correlation Matrix of Tau* `r knitr::kable(lower.tri.cor.matrix(alldat[,2:5]))`

```{r, echo=FALSE}
alldat$ln_slide12_slide13_diff <- alldat$ln_slide12.ao - alldat$ln_slide13.ao #S1-S2
alldat$slide12_slide13_diff <- alldat$slide12.ao - alldat$slide13.ao #S1-S2

alldat_diff <- alldat[c("ln_slide12_slide13_diff", "slide12_slide13_diff")]
stargazer(as.data.frame(alldat_diff), type = "text", title = "Summary of All Differences")
```

```{r t tests/regression on untransformed training data, echo=FALSE, include=FALSE}
# t test on differences

alldat.slide12_slide13.t.test <- t.test(alldat_diff$slide12_slide13_diff, mu = 0) 
alldat.ln.slide12_slide13.t.test <- t.test(alldat_diff$ln_slide12_slide13_diff, mu = 0) 
```

```{r, echo=FALSE, include=FALSE}
########### cv Calculations for Training Data-for verfication 
# Slide 2 - 3 Combinations 
# ln Transformed
alldat.ln.12.13.CV <- inter.assay.cv(alldat, ln_slide12.ao, ln_slide13.ao)
# Raw Transformed
alldat.raw.12.13.CV <- inter.assay.cv(alldat, slide12.ao, slide13.ao)

```

```{r AVG CV COMPARISION TRAINING DATA}
# ln Transformed
alldat.ln_avg.cv <- mean(alldat.ln.12.13.CV$pct.CV, na.rm = T)
# Raw
alldat.raw_avg.cv <- mean(alldat.raw.12.13.CV$pct.CV, na.rm = T)
```
```{r BA Plots - training data untransformed and transformed, echo=FALSE}
# Serial Intraassay - Run 2
# ln transformed values
alldat.ln.12.13.ba_stats <- bland.altman.stats(alldat$ln_slide12.ao , alldat$ln_slide13.ao)
alldat.ln.r2_s1.s2_ba_plot <- {plot(alldat.ln.12.13.ba_stats$means, alldat.ln.12.13.ba_stats$diffs,
     main="ln all Tau Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
  abline(h = alldat.ln.12.13.ba_stats$lines, col=c("red","blue","red"))}

# Raw values
alldat.raw.12.13.ba_stats <- bland.altman.stats(alldat$slide12.ao , alldat$slide13.ao)
alldat.r2_s1.s2_ba_plot <- {plot(alldat.raw.12.13.ba_stats$means, alldat.raw.12.13.ba_stats$diffs,
     main="Raw all Tau Data Serial Sections - Run 2 vs Run 3", pch = 19, xlab = "Means", ylab = "Differences")
  abline(h = alldat.raw.12.13.ba_stats$lines, col=c("red","blue","red"))}

alldat.ln.slide12_slide13.t.test
alldat.slide12_slide13.t.test
```